### 2015-12-13 paper/4-performance.tex
Remove windows from paper, since cygwin still is not c++11 compliant.

For all benchmarks, results are well within a 5\% deviation of the average, such that only the average is used in the remainder of this section.
The same compilation flags were used for both adevs and dxex benchmarks (``\texttt{-O3 -flto}'').
To guarantee comparable results, no I/O was performed during the benchmarking phase such that computation was CPU-bound.
Simulation traces are used to verify that both adevs and dxex models have exactly the same behaviour.
Benchmarks were performed using Linux, but our simulation tool works equally well on Windows and Mac.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/queue_sequential.eps}
	\caption{Queue benchmark results for sequential simulation.}
	\label{fig:Queue_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/interconnect_sequential.eps}
	\caption{Interconnect benchmark results for sequential simulation.}
	\label{fig:Interconnect_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{fig/queue_parallel.eps}
	\caption{Queue benchmark results for parallel simulation of a model of fixed size.}
	\label{fig:queue_benchmark_parallel}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/phold_voorlopig.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{fig/interconnect_parallel.eps}
    \caption{Interconnect benchmark results for parallel simulation.}
    \label{fig:interconnect_benchmark_parallel}
\end{figure}

>>>>

For all benchmarks, results are well within a 5\% deviation of the average, such that only the average is used in the remainder of this section.
The same compilation flags were used for both adevs and dxex benchmarks (``\texttt{-O3 -flto}'').
To guarantee comparable results, no I/O was performed during the benchmarking phase such that computation was CPU-bound.
Simulation traces are used to verify that both adevs and dxex models have exactly the same behaviour.
Benchmarks were performed using Linux, but our simulation tool works equally well on Mac.

@@

\begin{figure}
	\includegraphics[width=\columnwidth,height=6.5cm]{fig/queue_sequential.eps}
	\caption{Queue benchmark results for sequential simulation.}
	\label{fig:Queue_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth,height=6.5cm]{fig/interconnect_sequential.eps}
	\caption{Interconnect benchmark results for sequential simulation.}
	\label{fig:Interconnect_benchmark}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth,height=6.5cm]{fig/queue_parallel.eps}
	\caption{Queue benchmark results for parallel simulation of a model of fixed size.}
	\label{fig:queue_benchmark_parallel}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/phold_priority.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/interconnect_parallel.eps}
    \caption{Interconnect benchmark results for parallel simulation.}
    \label{fig:interconnect_benchmark_parallel}
\end{figure}
